### 2019-02-26 sections/relatedwork.tex
distinction between explicit and implicit formal semantics

There have been two previous papers that describe semantics of iTasks, by \citet{conf/ifl/KoopmanPA08} and \citet{conf/ppdp/PlasmeijerLMAK12}.
Both give a different semantics in the form of minimal implementations of a subset of the interface of iTasks.
These semantics however do not make an explicit distinction between the host language and task language and they do not provide a formal semantics, which makes formal reasoning difficult.

\fixme{Rinus: Volgens mij is er wel degelijk een formele semantiek, omdat heel iTask wordt uitgelegd in termen van standaard Clean functies,
en Clean heeft een semantiek (graaf herschrijf systeem).
Dat de beschrijving onhandig (wellicht te low level is) is voor het formeel redeneren over iTask programma's is een beter argument.}

>>>>

There have been two previous papers that describe semantics of iTasks, by \citet{conf/ifl/KoopmanPA08} and \citet{conf/ppdp/PlasmeijerLMAK12}.
Both give a different semantics in the form of minimal implementations of a subset of the interface of iTasks.
These semantics however do not make an explicit distinction between the host language and task language and they do not provide an explicit formal semantics.
\ITASKS implicitly has a formal semantics, inherited from the graph-rewriting semantics of Clean.
This semantics however does not lend itself well for formal reasoning.
